Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-06-04 PAPER.tex
dominating -> dominated

In general, the highest-valued eigenmodes of $\widehat{\textbf{C}}$ typically (but not always) describe bright foregrounds --- the most prominent shapes in a dataset. For these FG-dominating modes, where foregrounds outshine the EoR signal, down-weighting is beneficial. In some sense, we desire signal loss in this regime, if by `signal' we mean `foregrounds.' In this case it is beneficial for these eigenmodes to be coupled to the data in a way that produces loss. For our toy model, the successful suppression of the foreground mode is demonstrated in Figure \ref{fig:toy_sigloss3} by the missing foreground peak in the weighted power spectrum estimate (green).

@@

Altering $\widehat{\textbf{C}}$ as such is one specific example of a regularization method for this toy model, in which we are 
changing $\widehat{\textbf{C}}$ in a way that changes its coupling to the data realization. The resulting 
power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. In this case we recover the EoR signal, 
demonstrating that if we can disentangle the foreground-dominating modes and EoR-dominating modes, we can down-weight 
them with negligible signal loss. There are several other ways to regularize $\widehat{\textbf{C}}$, and we will discuss some in Section 
\ref{sec:otherweight}.

@@

The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} minimizes signal loss a different way --- 
by only using the first three eigenmodes of the estimated covariance. Recalling that our toy model foregrounds can be described entirely by the first eigenmode, this 
method intentionally projects out the highest-valued modes only by replacing all but the three highest weights in the 
eigenspectrum with $1$'s (equal weights). Again, avoiding the over-fitting of EoR-dominating modes which are coupled to the data results in negligible signal loss. However, we do 
not perfectly recover the shape of the EoR power spectrum because we lost information when ignoring the relative weights of most modes. While this case is illuminating for the toy model, in practice it is not obvious which eigenmodes are FG or EoR dominated (and they could be mixed as well), so determining which subset of modes to down-weight is not trivial.

>>>>

In general, the highest-valued eigenmodes of $\widehat{\textbf{C}}$ typically (but not always) describe bright foregrounds --- the most prominent shapes in a dataset. For these FG-dominated modes, where foregrounds outshine the EoR signal, down-weighting is beneficial. In some sense, we desire signal loss in this regime, if by `signal' we mean `foregrounds.' In this case it is beneficial for these eigenmodes to be coupled to the data in a way that produces loss. For our toy model, the successful suppression of the foreground mode is demonstrated in Figure \ref{fig:toy_sigloss3} by the missing foreground peak in the weighted power spectrum estimate (green).

@@

Altering $\widehat{\textbf{C}}$ as such is one specific example of a regularization method for this toy model, in which we are 
changing $\widehat{\textbf{C}}$ in a way that changes its coupling to the data realization. The resulting 
power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. In this case we recover the EoR signal, 
demonstrating that if we can disentangle the foreground-dominated modes and EoR-dominated modes, we can down-weight 
them with negligible signal loss. There are several other ways to regularize $\widehat{\textbf{C}}$, and we will discuss some in Section 
\ref{sec:otherweight}.

@@

The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} minimizes signal loss a different way --- 
by only using the first three eigenmodes of the estimated covariance. Recalling that our toy model foregrounds can be described entirely by the first eigenmode, this 
method intentionally projects out the highest-valued modes only by replacing all but the three highest weights in the 
eigenspectrum with $1$'s (equal weights). Again, avoiding the over-fitting of EoR-dominated modes which are coupled to the data results in negligible signal loss. However, we do 
not perfectly recover the shape of the EoR power spectrum because we lost information when ignoring the relative weights of most modes. While this case is illuminating for the toy model, in practice it is not obvious which eigenmodes are FG or EoR dominated (and they could be mixed as well), so determining which subset of modes to down-weight is not trivial.
